MSstatsPTM statistical relative quantification of post-translational modifications in bottom-up proteomic experiments

### 2022-05-31 main/MSstatsPTM_Main.tex
Small

\subsection*{Dataset 5 : Mouse - Phosphorylation - 2mix-TMT time series}
\label{sec:exp_proc_dataset5}
In this experiment 8 biological replicates were allocated to 2 TMT mixtures in an unbalanced time course design. More details are in Supplementary Sec. \ref{supp-sec:shigella}.

@@

\begin{figure}[h!]
\centering
\begin{subfigure}{\textwidth}
 \centering
\includegraphics[height=.5\textwidth]{images/shig_venn_diagramm.png}
\caption{}
\label{fig:data5_venn_diagram}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=1.0\textwidth]{images/No_Difference_Shigella_Profile_Plot}
	\caption{}
	\label{fig:data5_profile_plot}
	 \end{subfigure}
\caption{Dataset 5 : Mouse - Phosphorylation - 2mix-TMT time series. a) The overlap of differentially modified peptides between the PTM model with and without global protein level adjustment. Again more PTMs became insignificant after adjustment then became significant. b) Comparing the global profiling of protein $TTP$ with the modification of the protein at site $S178$. When looking at the summary of the modification and global protein it was clear the difference between conditions followed the same trend. Specifically, there was a positive adjustment in abundance when comparing WT\_Uninfect to WT\_Late in both the modification and global profiling run. This indicated the movement was driven by changes in global protein that was only accounted for in the model after adjusting for global protein abundance change.}
\label{fig:data5_plots}
\end{figure}

>>>>

\subsection*{Dataset 5 : Mouse - Phosphorylation - 2mix-TMT time series}
\label{sec:exp_proc_dataset5}
\todo{For each experimental dataset, could you say how many proteins were quantified, and the average number of {SM per protein (modified/unmodified)? I was looking everywhere and could not find the info} In this experiment 8 biological replicates were allocated to 2 TMT mixtures in an unbalanced time course design. More details are in Supplementary Sec. \ref{supp-sec:shigella}.

@@

\begin{figure}[h!]
\centering
\begin{subfigure}{\textwidth}
 \centering
\includegraphics[height=.5\textwidth]{images/shig_venn_diagramm.png}
\caption{}
\label{fig:data5_venn_diagram}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=1.0\textwidth]{images/No_Difference_Shigella_Profile_Plot}
	\caption{}
	\label{fig:data5_profile_plot}
	 \end{subfigure}
\caption{Dataset 5 : Mouse - Phosphorylation - 2mix-TMT time series. \todo{OV: What are the vertical panels 1 and 2 in (b)?? Are they bio reps? Could you clarify? I would remove the work 'BioReplicate' at the bottom, it is not clear what it refers to} a) The overlap of differentially modified peptides between the PTM model with and without global protein level adjustment \todo{OV: in which pairwise comparison? Across all the comparisons?}. Again more PTMs became insignificant after adjustment then became significant. b) Comparing the global profiling of protein $TTP$ with the modification of the protein at site $S178$. When looking at the summary of the modification and global protein it was clear the difference between conditions followed the same trend. Specifically, there was a positive adjustment in abundance when comparing WT\_Uninfect to WT\_Late in both the modification and global profiling run. This indicated the movement was driven by changes in global protein that was only accounted for in the model after adjusting for global protein abundance change.}
\label{fig:data5_plots}
\end{figure}
